### 2013-08-21 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
adding edits to spn chapter

yields the $SP_3$ equations).

\subsection{Eigenvalue Form of the $SP_N$ Equations}
\label{subsec:eigenvalue_form}
For criticality problems, the space, angle, and energy discretizations
for the $SP_N$ equations can be applied to the general eigenvalue form
of the transport equation given by
Eq~(\ref{eq:eigenvalue_transport}). We can readily replace the fixed
source in Eq~(\ref{eq:spn_matrix}) with a fission source this time
considering the multigroup form of the $SP_N$ equations derived in
Appendix~\ref{chap:mg_spn_equations}:
\begin{multline}
  -\nabla \cdot \Bigg[\frac{n}{2n+1}\mathbf{\Sigma_{n-1}}^{-1} \nabla
    \Big(\frac{n-1}{2n-1} \mathbf{\Phi_{n-2}} +
    \frac{n}{2n-1}\mathbf{\Phi_n} \Big) \\+
    \frac{n+1}{2n+1}\mathbf{\Sigma_{n+1}}^{-1} \nabla
    \Big(\frac{n+1}{2n+3}\mathbf{\Phi_n} +
    \frac{n+2}{2n+3}\mathbf{\Phi_{n+2}}\Big) \Bigg] \\+
  \mathbf{\Sigma_n} \mathbf{\Phi_n} = \frac{1}{k} \mathbf{F}
  \mathbf{\Phi_n} \delta_{n0} \ \ \ \ \ \ \ \ \ n = 0,2,4,\cdots,N\:.
  \label{eq:multigroup_spn_eigenvalue}
\end{multline}
with the fission matrix $\mathbf{F}$ given by
\cite{evans_simplified_2013}. We again apply the change of variables to
yield the set of multigroup pseudo-moments $\mathbb{U}_n$ where now
the application of the fission matrix to the moment vectors will be
expanded into a set of block matrices in identical fashion to the
scattering matrices:
\begin{equation}
  -\nabla \cdot \mathbb{D}_n \nabla \mathbb{U}_n + \sum_{m=1}^4
  \mathbb{A}_{nm} \mathbb{U}_m = \frac{1}{k} \sum_{m=1}^4
  \mathbb{F}_{nm} \mathbb{U}_m\ \ \ \ \ \ \ n = 1,2,3,4\:.
  \label{eq:spn_fission_matrix}
\end{equation}
It should be noted here that with respect to a general MCSA scheme,
the introduction of fission in the system will only affect the source
vector in the linear system. The linear operator, and therefore
overall MCSA performance will be dictated by streaming and scattering
as defined on the left-hand side.

>>>>

yields the $SP_3$ equations). For these equations, the $SP_N$ order
defines the largest order flux moment maintained in the calculation
and the $P_N$ order defines the largest order of the cross section
expansion maintained.

\subsection{Eigenvalue Form of the $SP_N$ Equations}
\label{subsec:eigenvalue_form}
For criticality problems, the space, angle, and energy discretizations
for the $SP_N$ equations can be applied to the general eigenvalue form
of the transport equation given by
Eq~(\ref{eq:eigenvalue_transport}). We can readily replace the fixed
source in Eq~(\ref{eq:spn_matrix}) with a fission source this time
considering the multigroup form of the $SP_N$ equations derived in
Appendix~\ref{chap:mg_spn_equations}:
\begin{multline}
  -\nabla \cdot \Bigg[\frac{n}{2n+1}\mathbf{\Sigma_{n-1}}^{-1} \nabla
    \Big(\frac{n-1}{2n-1} \mathbf{\Phi_{n-2}} +
    \frac{n}{2n-1}\mathbf{\Phi_n} \Big) \\+
    \frac{n+1}{2n+1}\mathbf{\Sigma_{n+1}}^{-1} \nabla
    \Big(\frac{n+1}{2n+3}\mathbf{\Phi_n} +
    \frac{n+2}{2n+3}\mathbf{\Phi_{n+2}}\Big) \Bigg] \\+
  \mathbf{\Sigma_n} \mathbf{\Phi_n} = \frac{1}{k} \mathbf{F}
  \mathbf{\Phi_n} \delta_{n0} \ \ \ \ \ \ \ \ \ n = 0,2,4,\cdots,N\:.
  \label{eq:multigroup_spn_eigenvalue}
\end{multline}
with the fission matrix $\mathbf{F}$ given by
\cite{evans_simplified_2013}. We again apply the change of variables to
yield the set of multigroup pseudo-moments $\mathbb{U}_n$ where now
the application of the fission matrix to the moment vectors will be
expanded into a set of block matrices in identical fashion to the
scattering matrices:
\begin{equation}
  -\nabla \cdot \mathbb{D}_n \nabla \mathbb{U}_n + \sum_{m=1}^4
  \mathbb{A}_{nm} \mathbb{U}_m = \frac{1}{k} \sum_{m=1}^4
  \mathbb{F}_{nm} \mathbb{U}_m\ \ \ \ \ \ \ n = 1,2,3,4\:.
  \label{eq:spn_fission_matrix}
\end{equation}
It should be noted here that with respect to a general MCSA scheme,
the introduction of fission in the system will only affect the source
vector in the linear system for the eigenvalue schemes used in this
work. The linear operator, and therefore overall MCSA performance will
be dictated by streaming and scattering as defined on the left-hand
side.
